
\documentclass[10pt]{article}
\usepackage{fontspec}                       %for loading fonts
\usepackage{xunicode,xltxtra,url,parskip}   %other packages for formatting
    \RequirePackage{color,graphicx}
\usepackage{multicol}
    \setlength{\columnsep}{0.5cm}
\usepackage{titlesec}
\usepackage{hyperref}                       %Setup hyperref package, and colours for links
    \definecolor{linkcolour}{rgb}{0,0.2,0.6}
    \hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}
\usepackage{vwcol}\setlength{\columnsep}{-1.0cm}
\usepackage[
    paperheight=14.4in,
    paperwidth=9.0in,
    top=0.3in,
    bottom=0.2in,
    right=0.3in,
    left=0.3in]{geometry}
\usepackage{enumitem}

%FONTS
\defaultfontfeatures{Mapping=tex-text}
\setmainfont[Path=Fonts/,
    SmallCapsFont={Fontin-SmallCaps.otf},
    BoldFont={Fontin-Bold.otf},
    ItalicFont={Fontin-Italic.otf}
    ]{Fontin.otf}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}

% Set col seperate length
\setlength{\columnsep}{0.01cm}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}
    \pagestyle{empty}       % non-numbered pages
    \font\fb=''[cmr10]''    %for use with \LaTeX command

    %--------------------TITLE-------------
    \begin{multicols}{2}
        \begin{flushleft}
            \textbf{{\Huge Dang Le Dang Khoa }}
            % \vspace{3mm}
            % \emph{\large Language Proficiency:} \textbf{\large Python, C/C++, Bash/Linux}
        \end{flushleft}

        \columnbreak

        \begin{flushright}
            \normalsize (+65) 8398 3951 \\
            \href{mailto:dangledangkhoa@gmail.com}{dangledangkhoa@gmail.com} \\
            \href{https://github.com/dangkhoadl}{github.com/dangkhoadl} \\
            \href{https://sg.linkedin.com/in/dangledangkhoa}{linkedin.com/in/dangledangkhoa}
        \end{flushright}
    \end{multicols}

    %--------------------SECTIONS-----------------------------------
     % ------------------------- Section: Work Experience -------------------------------
    \vspace{-8mm}
    \section{Technical Skills}
    \begin{itemize}[noitemsep,leftmargin=*]
        \item \textbf{Languages}: Python (Pandas, Matplotlib, Numpy, Scikit-learn, Pytorch, Keras, PySpark), C/C++ (STL, Libtorch, OpenMP), Bash/Linux (shell scripting, awk, Dockerfile)
        \item \textbf{Tools}: kaldi-asr, ESPnet-e2e, jupyter notebook, git, huggingface
    \end{itemize}

    % ------------------------- Section: Work Experience -------------------------------
    \vspace{2mm}
    \section{Experience (selected)}
        \vspace{-2mm}

        % --------------- Entry ----------------------------------
        \begin{multicols}{3}
            \begin{flushleft}
                \textbf{Research Engineer}
            \end{flushleft}

            \columnbreak

            \begin{center}
                \textbf{Institute for Infocomm Research - A*STAR}
            \end{center}

            \columnbreak

            \begin{flushright}
                \textbf{February 2020 - Present}
            \end{flushright}
        \end{multicols}

        \vspace{-5mm}
        \emph{Speech-to-text (Automatic Speech Recognition) field}
        \vspace{-2.5mm}
        \begin{itemize}[noitemsep]
            \item Trained and maintained Bahasa Malay core Speech-to-Text engine and language model, improved Word-Error-Rate by 10\% from the baseline model.
            \item Integrated and finetuned Singapore English ASR engine into domain-specific services, including Legal, Healthcare, and Education.
            \item Transformed and augmented audio and text data for model training.
        \end{itemize}

        \emph{Natural Language Processing - Audio Analytics and Classifications field}
        \vspace{-2.5mm}
        \begin{itemize}[noitemsep]
            \item Trained and integrated \emph{ECAPA-TDNN} deep learning model for speaker diarization service, meeting minute note-taking application.
            \item Trained \emph{U-net} audio enhancement model for Satellite-based VHF communication; performance improved by 3\% compared to RNN baseline model.
            \item Modeled sentence embedding inference and logic backend for Vietnamese-voiced FAQ chatbot.
            \item Contributed to other team-scaled \emph{Natural Language Processing} and \emph{Classification} tasks: Sentiment Analysis, Embedded Sound Classification, and Text Processing.
        \end{itemize}

        % --------------- Entry ----------------------------------
        \begin{multicols}{3}
            \begin{flushleft}
                \textbf{Researcher}
            \end{flushleft}

            \columnbreak

            \begin{center}
                \textbf{Satellite Research Centre}
            \end{center}

            \columnbreak

            \begin{flushright}
                \textbf{August 2016 - August 2018}
            \end{flushright}
        \end{multicols}

        \vspace{-5mm}
        % \begin{itemize}[noitemsep,leftmargin=*]
        \begin{itemize}[noitemsep]
            \item Implemented a novel Star Tracking Algorithm onto a Programmable System-on-a-chip for mini satellites.
            \item Optimized the pattern recognition algorithm runtime, improved the accuracy by 5\% on average.
            \item Designed a tree-based pattern searching algorithm, improved runtime processing by 25\%.
        \end{itemize}

    % ------------------------- Section: Competitions -------------------------------
    \vspace{2mm}
    \section{Honors \& awards (selected)}
    \vspace{-2mm}
        % --------------- Entry ----------------------------------
        \begin{multicols}{1}
            \begin{flushleft}
                \textbf{AI Singapore - Trusted Media Challenge 2021}
            \end{flushleft}
        \end{multicols}
        \vspace{-5mm}
        \begin{itemize}[noitemsep]
            \item Challenged for the detection of audio-visual fake media, a competition hosted by AI Singapore, sponsored by Singapore Press Holdings Ltd. with prize monies of up to SGD 700,000.
            \item Lead and contributed chief engineering work for \textbf{aasrali} team to compete with other 474 teams.
            \item Ranked 6th on the final stage leaderboard - Top 1\% teams - \href{https://trustedmedia.aisingapore.org/competition/aisg/final-leaderboard/}{Final Round Leaderboard}.
        \end{itemize}

        % --------------- Entry ----------------------------------
        \begin{multicols}{1}
            \begin{flushleft}
                \textbf{ConferencingSpeech 2021 Challenge}
            \end{flushleft}
        \end{multicols}
        \vspace{-5mm}
        \begin{itemize}[noitemsep]
            \item Challenged for Far-field Multi-Channel Speech Enhancement for Video Conferencing, hosted by Interspeech and Tencent Ethereal Audio Lab.
            \item Ranked in top 10 with I2R-ALI team.
        \end{itemize}
        % --------------- Entry ----------------------------------
        \begin{multicols}{1}
            \begin{flushleft}
                \textbf{Google Code Jam 2018}
            \end{flushleft}
        \end{multicols}
        \vspace{-5mm}
        \begin{itemize}[noitemsep]
        \item Competed individually in the problem solving contest organized annually by Google with over 27,000 competitors.
        \item Advanced to round 2 - Top 10\% candidates.
        \end{itemize}

    % ------------------------- Section: Education -------------------------------
    \vspace{2mm}
    \section{Education}
        \vspace{-2mm}
        % --------------- Entry ----------------------------------
        \begin{multicols}{3}
            % \begin{flushleft}
                \textbf{Master of Engineering}
            % \end{flushleft}

            \columnbreak

            % \begin{center}
                \textbf{Nanyang Technological University Singapore}
            % \end{center}

            \columnbreak

            \begin{flushright}
                \textbf{August 2015 - August 2018}
            \end{flushright}
        \end{multicols}

        \vspace{-5mm}
        \begin{itemize}[noitemsep]
            \item School of Electrical and Electronics Engineering - Research.
            \item \textsc{Thesis title}: Implementation of An Autonomous Star Recognition Algorithm using Hardware-Software Co-Processing Approach.
            \item \emph{Source code}: \href{https://git.io/vpucY}{git.io/vpucY}
            \item \emph{Publication}: \href{https://doi.org/10.32657/10220/48371}{https://doi.org/10.32657/10220/48371}
        \end{itemize}
        \vspace{-2mm}

        % --------------- Entry ----------------------------------
        \begin{multicols}{3}
            \begin{flushleft}
                \textbf{Bachelor of Engineering}
            \end{flushleft}

            \columnbreak

            \begin{center}
                \textbf{Vietnam National University}
            \end{center}

            \columnbreak

            \begin{flushright}
                \textbf{August 2010 - April 2015}
            \end{flushright}
        \end{multicols}

        \vspace{-5mm}
        \begin{itemize}[noitemsep]
            \item Ho Chi Minh City University of Technology - Second Upper Honour.
            \item Major: Electrical and Electronics Engineering, Minor: Automation System Design.
            \item \textsc{Thesis title}: Applying of Fuzzy Logic Algorithm on Legged Locomotion Robot.
        \end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % \newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % ------------------------- Section: Projects -------------------------------
    \vspace{2mm}
    \section{Open-Source Projects (selected)}
        \vspace{-2mm}
        % --------------- Entry ----------------------------------
        \begin{multicols}{1}
            \begin{flushleft}
                \textbf{WER-in-CPP}
            \end{flushleft}
        \end{multicols}
        \vspace{-5mm}
        \begin{itemize}[noitemsep]
            \item Developed an open-source API to calculate Word-Error-Rate for ASR project based on Minimum-Edit-Distance Dynamic Programming problem.
            \item Added the new features of text-based visualization and WER-per-utterance for statistical analysis.
            \item \emph{Source code}: \href{https://github.com/dangkhoadl/WER-in-cpp}{https://github.com/dangkhoadl/WER-in-cpp}
        \end{itemize}
        \vspace{-2mm}

        % --------------- Entry ----------------------------------
        \begin{multicols}{1}
            \begin{flushleft}
                \textbf{Machine Learning and Algorithms Repositories}
            \end{flushleft}
        \end{multicols}
        \vspace{-5mm}
        \begin{itemize}[noitemsep]
            \item Maintain GitHub repositories for personal note-taking, introducing and mentoring students to Data Structures - Algorithms, and Machine Learning.
            \item Solved multiple problems in Computer science (Traveling Salesman, Stable Marriage Matching, etc.) and Machine Learning (Random Walks, AI bot playing the trending mobile game \emph{Lyto Different Color}).
            \item \emph{Source code}: \href{https://github.com/dangkhoadl?tab=repositories}{https://github.com/dangkhoadl}
        \end{itemize}
        \vspace{-2mm}

    % ------------------------- Section: Certificates -------------------------------
    \vspace{2mm}
    \section{Certifications (selected)}
        % \vspace{-2mm}
    \begin{itemize}[noitemsep,leftmargin=*]
        \item \textsc{Coursera - Discrete Optimization - } \href{https://www.coursera.org/account/accomplishments/verify/YXTNUBC3G3LX}{Certificate}
        \item \textsc{Coursera - Machine Learning Specialization - } \href{https://www.coursera.org/account/accomplishments/specialization/3P6TZYWVJKHY}{Certificate}
        \item \textsc{Coursera - Data Structures and Algorithms Specialization - } \href{https://www.coursera.org/account/accomplishments/specialization/AKFYZQ9QD8XH}{Certificate}
        \item \textsc{Udacity - Machine Learning Engineer Nanodegree - } \href{https://graduation.udacity.com/confirm/HK9JLR3N}{Certificate}
    \end{itemize}
\end{document}
