

\documentclass[10pt]{article}
\usepackage{fontspec}                       %for loading fonts
\usepackage{xunicode,xltxtra,url,parskip}   %other packages for formatting
    \RequirePackage{color,graphicx}
\usepackage{multicol}
\usepackage{titlesec}
\usepackage{hyperref}                       %Setup hyperref package, and colours for links
    \definecolor{linkcolour}{rgb}{0,0.2,0.6}
    \hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}
\usepackage{vwcol}\setlength{\columnsep}{2.0cm}
\usepackage[
    paperheight=11.0in,
    paperwidth=8.5in,
    top=0.3in,
    bottom=0.2in,
    right=0.3in,
    left=0.3in]{geometry}
\usepackage{enumitem}

%FONTS
\defaultfontfeatures{Mapping=tex-text}
\setmainfont[
    SmallCapsFont = Fontin-SmallCaps.otf,
    BoldFont = Fontin-Bold.otf,
    ItalicFont = Fontin-Italic.otf
]
{Fontin.otf}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}

% Set col seperate length
\setlength{\columnsep}{0.01cm}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}
    \pagestyle{empty}       % non-numbered pages
    \font\fb=''[cmr10]''    %for use with \LaTeX command

    %--------------------TITLE-------------
    \begin{multicols}{2}
        \begin{flushleft}
            \textbf{{\Huge Dang Le Dang Khoa }} \\
            \vspace{2mm}
            \emph{Language Proficiency:} \textbf{Python, C/C++, Bash, SQL}
        \end{flushleft}

        \columnbreak

        \begin{flushright}
            \textsc (+65) 8398 3951 \\
            \href{mailto:dangledangkhoa@gmail.com}{dangledangkhoa@gmail.com} \\
            \href{https://github.com/dangkhoadl}{github.com/dangkhoadl} \\
            \href{https://sg.linkedin.com/in/dangledangkhoa}{linkedin.com/in/dangledangkhoa}
        \end{flushright}
    \end{multicols}


    %--------------------SECTIONS-----------------------------------
    % ------------------------- Section: Work Experience -------------------------------
    \vspace{-5mm}
    \section{Professional Experience (selected)}
        % \vspace{-5mm}

        % --------------- Entry ----------------------------------
        \begin{multicols}{3}
            \begin{flushleft}
                \textbf{Research Engineer}
            \end{flushleft}

            \columnbreak

            \begin{center}
                \textbf{Institute for Infocomm Research - A*STAR}
            \end{center}

            \columnbreak

            \begin{flushright}
                \textbf{February 2020 - Present}
            \end{flushright}
        \end{multicols}

        \vspace{-5mm}
        \emph{Speech-to-text engines:}
        \vspace{-2.5mm}

        \begin{itemize}[noitemsep]
        \item Bahasa Malay Automatic-Speech-Recognition (ASR) - Core ASR Engine project
        \setlist{nolistsep}
            \begin{itemize}[noitemsep]
                \item Train and maintain deep learning Speech-to-Text and language model, improve 10\% in terms of word-error-rate (WER) compared to the former production model.
                \item Clean and maintain Malay language data, including audio, text, dictionary formats.
                \item Explore industrial applications of state-of-the art transformer-based, end-to-end Speech-to-Text engines.
            \end{itemize}
        \item Air Traffic Control (ATC) ASR
            \begin{itemize}[noitemsep]
                \item Pre-process and prepare raw audio/text data for training.
                \item Apply speech enhancement model to denoise audio data for other subsequence tasks:
                    \begin{enumerate}[noitemsep]
                        \item Enhance Voice activity detection (VAD).
                        \item Enhance raw Audio quality for labeling task.
                        \item Enhance output Audio quality to improve client listening experience.
                    \end{enumerate}
            \end{itemize}
        \item Legal-domain ASR
            \begin{itemize}[noitemsep]
                \item Pre-process and prepare raw audio, text data for model training (remove bad quality audios, parse legal-specific documents to cleaned text data).
                \item Benchmark and evaluate final production models.
                \item Visualize model efficiency and data statistics to end-user.
            \end{itemize}
            \item \emph{Toolkits}: \textbf{kaldi, Espnet, flashlight-wav2letter, Docker}
        \end{itemize}


        \emph{Natural Language Processing - Audio Analytics and Classifications:}
        \vspace{-2.5mm}
        \begin{itemize}[noitemsep]
            \item Speech enhancement deep learning model
                \begin{itemize}[noitemsep]
                    \item Implement bi-LSTM Densenet and U-net models.
                    \item Train with LibriSpeech, VoxCeleb, Aishell, MUSAN datasets.
                    \item Apply the model to denoise Air Traffic Control Audio data, improve noised audio quality by 25\% in terms of snr, pesq, and stoi.
                \end{itemize}
            \item Speech classification applications
                \begin{itemize}[noitemsep]
                    \item Train vector embedding and classifier to identify Covid-19 patients from coughing sound, resulting auc = 0.85.
                    \item Train model to classify deep-faked audios from authentic audios.
                \end{itemize}
            \item \emph{Toolkits}: \textbf{PyTorch, XGBoost, Scipy stacks}
        \end{itemize}


        \emph{Others tasks:}
        \vspace{-2.5mm}
        \begin{itemize}[noitemsep]
            \item Build and maintain training pipeline and docker templates for the team.
            \item Train new staff and exchange experience on ASR engine, data wrangling \& collecting, and PyTorch framework topics.
        \end{itemize}

        % --------------- Entry ----------------------------------
        \begin{multicols}{3}
            \begin{flushleft}
                \textbf{Researcher}
            \end{flushleft}

            \columnbreak

            \begin{center}
                \textbf{Satellite Research Centre}
            \end{center}

            \columnbreak

            \begin{flushright}
                \textbf{August 2016 - August 2018}
            \end{flushright}
        \end{multicols}

        \vspace{-5mm}

        $\bullet$ {Implemented a design of Star Tracking Algorithms onto a Programmable System-on-a-chip system. } \\
        $\bullet$ {Optimized the pattern recognition algorithm runtime by implementing the connected component labeling algorithm on parallel processors. Runtime is improved 64\% on average compared to traditional processor approach.} \\
        $\bullet$ {Optimized and designed the pattern searching algorithm by applying k-ary tree data structure. Time complexity and runtime improved 31\%, but space complexity and memory increased 22\%.} \\
        \emph{Source code}: \href{https://git.io/vpucY}{git.io/vpucY} \\
        \emph{Publication}: \href{https://doi.org/10.32657/10220/48371}{https://doi.org/10.32657/10220/48371}


    % ------------------------- Section: Education -------------------------------
    \vspace{2mm}
    \section{Education}
        % \vspace{-5mm}

        % --------------- Entry ----------------------------------
        \begin{multicols}{3}
            \begin{flushleft}
                \textbf{Master of Engineering}
            \end{flushleft}

            \columnbreak

            \begin{center}
                \textbf{Nanyang Technological University}
            \end{center}

            \columnbreak

            \begin{flushright}
                \textbf{August 2015 - August 2018}
            \end{flushright}
        \end{multicols}

        \vspace{-5mm}

        $\bullet$ {School of Electrical and Electronics Engineering - Research.} \\
        $\bullet$ \textsc{Thesis title}: Implementation of An Autonomous Star Recognition Algorithm using Hardware-Software Co-Processing Approach.


        % --------------- Entry ----------------------------------
        \begin{multicols}{3}
            \begin{flushleft}
                \textbf{Bachelor of Engineering}
            \end{flushleft}

            \columnbreak

            \begin{center}
                \textbf{Vietnam National University HCMC}
            \end{center}

            \columnbreak

            \begin{flushright}
                \textbf{August 2010 - April 2015}
            \end{flushright}
        \end{multicols}

        \vspace{-5mm}

        $\bullet$ {Ho Chi Minh City University of Technology - Electrical and Electronics Engineering - Second Upper Honour.} \\
        $\bullet$ {Major in Automation and Control engineering, minor in Robotics and Embedded System Design.} \\
        $\bullet$ \textsc{Thesis title}: Applying of Fuzzy Logic Algorithm on Legged Locomotion Robot.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % ------------------------- Section: Competitions -------------------------------
    \vspace{2mm}
    \section{Competition Achievements}
        % --------------- Entry ----------------------------------
        \begin{flushleft}
            \textbf{AI Singapore - Trusted Media Challenge 2021}
        \end{flushleft}
        \vspace{-1.5mm}
        $\bullet$ A Challenge for the detection of audiovisual fake media, hosted by AI Singapore, sponsored by Singapore Press Holdings Ltd. with prize monies of up to SGD 700,000. \\
        $\bullet$ Engineering and Team Lead of \textbf{aasrali} team to compete with other 474 teams. \\
        $\bullet$ Ranked 6th on the final stage leaderboard - \href{https://trustedmedia.aisingapore.org/competition/aisg/final-leaderboard/}{trustedmedia.aisingapore.org/competition/aisg/final-leaderboard}. \\

        % --------------- Entry ----------------------------------
        % \vspace{-2mm}
        \begin{flushleft}
            \textbf{Google Code Jam 2018}
        \end{flushleft}
        \vspace{-1.5mm}
        $\bullet$ An algorithm problem solving contest organized annually by Google with over 27,000 competitors. \\
        $\bullet$ Round 2 qualifier - Top 10\% Candidates. \\

        % --------------- Entry ----------------------------------
        \begin{flushleft}
            \textbf{ConferencingSpeech 2021 Challenge}
        \end{flushleft}
        \vspace{-1.5mm}
        $\bullet$ A Challenge for Far-field Multi-Channel Speech Enhancement for Video Conferencing, hosted by Interspeech and Tencent Ethereal Audio Lab. \\
        $\bullet$ Member of I2R-ALI team - Top 10 ranking team. \\


    % ------------------------- Section: Projects -------------------------------
    \vspace{2mm}
    \section{Open-Source Projects (selected)}
        % \vspace{-2mm}
        % --------------- Entry ----------------------------------
        \begin{flushleft}
            \textbf{WER-in-CPP}
        \end{flushleft}
        \vspace{-1.5mm}
        $\bullet$ Develop an open-source API to calculate Word-Error-Rate for ASR project based on Minimum-Edit-Distance problem. \\
        $\bullet$ Develop new features compared to existing kaldi code: Provide WER-per-utterance utilizing upon dataset statistical analysis. \\    
            \emph{Technologies}: \textbf{C++} \\
            \emph{Source code}: \href{https://github.com/dangkhoadl/WER-in-cpp}{https://github.com/dangkhoadl/WER-in-cpp} \\

        % --------------- Entry ----------------------------------
        \begin{flushleft}
            \textbf{Problem Solving}
        \end{flushleft}
        \vspace{-1.5mm}
        $\bullet$ Solve Computer Science and Competitive Programming Problems. \\
        	\emph{Source code}: \href{https://github.com/dangkhoadl/my-CS-Notebook}{https://github.com/dangkhoadl/my-CS-Notebook} \\
        $\bullet$ Solve Machine Learning Problems. \\
        	\emph{Source code}: \href{https://github.com/dangkhoadl/my-Machine-Learning}{https://github.com/dangkhoadl/my-Machine-Learning} \\


    % ------------------------- Section: Certificates -------------------------------
    \vspace{2mm}
    \section{Certificates and Related Courseworks}
        % \vspace{-2mm}

        $\bullet$ \textsc{Coursera - \href{https://www.coursera.org/account/accomplishments/specialization/certificate/AKFYZQ9QD8XH}{Data Structures and Algorithms Specialization}}, \textsc{\href{https://www.coursera.org/account/accomplishments/specialization/certificate/ZUGAFYKCMQ79}{Machine Learning Specialization}}, \textsc{\href{https://www.coursera.org/account/accomplishments/specialization/certificate/N3D6C3DT8QAY?utm_medium=certificate&utm_source=link&utm_campaign=copybutton_certificate}{Mathematics for Machine Learning}}, \textsc{\href{https://www.coursera.org/account/accomplishments/certificate/XN2B7T4AJX8C}{Introduction to Deep Learning}}, \textsc{\href{https://www.coursera.org/account/accomplishments/certificate/G25TQPPNXGW5}{Big Data Essentials: HDFS, MapReduce, and Spark RDD}} \\
        $\bullet$ \textsc{Udacity - \href{https://graduation.udacity.com/confirm/HK9JLR3N}{Machine Learning Engineer Nanodegree}} \\
        % $\bullet$ \textsc{Udacity - \href{https://graduation.udacity.com/confirm/KPSCQGZK}{Full Stack Web Developer Nanodegree}} \\
        $\bullet$ \textsc{MIT-6.041-Probabilistic Systems Analysis and Applied Probability} \\
        $\bullet$ \textsc{UC Berkeley - CS162 - Operating Systems and Systems Programming} \\
        $\bullet$ \textsc{UIUC - CS425 - Distributed Systems}

\end{document}
