

\documentclass[10pt]{article}
\usepackage{fontspec}                       %for loading fonts
\usepackage{xunicode,xltxtra,url,parskip}   %other packages for formatting
    \RequirePackage{color,graphicx}
\usepackage{multicol}
\usepackage{titlesec}
\usepackage{hyperref}                       %Setup hyperref package, and colours for links
    \definecolor{linkcolour}{rgb}{0,0.2,0.6}
    \hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}
\usepackage{vwcol}\setlength{\columnsep}{2.0cm}
\usepackage[
    paperheight=11.2in,
    paperwidth=8.5in,
    top=0.3in,
    bottom=0.5in,
    right=0.3in,
    left=0.3in]{geometry}

%FONTS
\defaultfontfeatures{Mapping=tex-text}
\setmainfont[
    SmallCapsFont = Fontin-SmallCaps.otf,
    BoldFont = Fontin-Bold.otf,
    ItalicFont = Fontin-Italic.otf
]
{Fontin.otf}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}

% Set col seperate length
\setlength{\columnsep}{0.01cm}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}
    \pagestyle{empty}       % non-numbered pages
    \font\fb=''[cmr10]''    %for use with \LaTeX command

    %--------------------TITLE-------------
    \begin{multicols}{2}
        \begin{flushleft}
            \textbf{{\Huge Dang Le Dang Khoa }}
        \end{flushleft}

        \columnbreak

        \begin{flushright}
            \textsc (+84) 93 863 7642 \\
            \href{mailto:dangledangkhoa@gmail.com}{dangledangkhoa@gmail.com} \\
            \href{https://github.com/dangkhoadl}{github.com/dangkhoadl} \\
            \href{https://sg.linkedin.com/in/dangledangkhoa}{linkedin.com/in/dangledangkhoa}
        \end{flushright}
    \end{multicols}

    \vspace{-5mm}

    %--------------------SECTIONS-----------------------------------
    % ------------------------- Section: Work Experience -------------------------------
    \section{Work Experience (selected)}
        \vspace{-5mm}

        % --------------- Entry ----------------------------------
        \begin{multicols}{3}
            \begin{flushleft}
                \textbf{Master of Engineering Candidate}
            \end{flushleft}

            \columnbreak

            \begin{center}
                \textbf{Satellite Research Centre}
            \end{center}

            \columnbreak

            \begin{flushright}
                \textbf{August 2016 - August 2018}
            \end{flushright}
        \end{multicols}

        \vspace{-5mm}

        $\bullet$ {Implemented a design of Star Tracking Algorithms onto a Programmable System-on-a-chip system. }\\
        $\bullet$ {Optimized the pattern recognition algorithm runtime by implementing the connected component labeling algorithm on parallel processors. Runtime is improved 64\% on average compared to traditional processor approach.} \\
        $\bullet$ {Optimized and designed the pattern searching algorithm by applying k-ary tree data structure. Time complexity and runtime improved 31\%, but space complexity and memory increased 22\%.} \\
        \emph{Languages/Technologies}: \textbf{C/C++, Python, Bash}\\
        \emph{Source code}: \href{https://git.io/vpucY}{git.io/vpucY}


    % ------------------------- Section: Projects -------------------------------
    \section{Projects (selected)}
        \vspace{-2mm}

        % --------------- Entry ----------------------------------
        \begin{center}
            \textbf{Dota 2 Hero Recommendation}
        \end{center}
        $\bullet$ {Recommended game characters based on historical user data collected by Open Dota API.} \\
        \emph{Languages/Technologies}: \textbf{Python, flask, pandas, numpy.} \\
        \emph{Source code}: \href{https://git.io/fhV1q}{git.io/fhV1q}


        % --------------- Entry ----------------------------------
        \begin{center}
            \textbf{Stock Price Predictor}
        \end{center}
        $\bullet$ {Predicted Time-series data by Linear Regression and ARIMA modeling approaches.} \\
        $\bullet$ {Optimized Model's accuracy by 20\% by performing feature engineerings and hyper-parameters optimizations.} \\
        $\bullet$ {Evaluated and Benchmarked models based on Root Mean Squared Error Metrics.} \\
        \emph{Languages/Technologies}: \textbf{Python, pandas, numpy, matplotlib, sklearn.} \\
        \emph{Source code}: \href{https://git.io/vpuCA}{git.io/vpuCA}


        % --------------- Entry ----------------------------------
        \begin{center}
            \textbf{Neighborhood Map APIs}
        \end{center}
        $\bullet$ {Built a neighborhood map based on Google Map, Wikipedia, Foursquare APIs.} \\
        $\bullet$ {Deployed and Configured Amazon Linux servers.} \\
        \emph{Languages/Technologies}: \textbf{Javascript, Flask, Ajax, jQuery, Knockout.} \\
        \emph{Source code}: \href{https://git.io/fhVMf}{git.io/fhVMf}


    % ------------------------- Section: Education -------------------------------
    \section{Education}
        \vspace{-5mm}

        % --------------- Entry ----------------------------------
        \begin{multicols}{3}
            \begin{flushleft}
                \textbf{Master of Engineering}
            \end{flushleft}

            \columnbreak

            \begin{center}
                \textbf{Nanyang Technological University}
            \end{center}

            \columnbreak

            \begin{flushright}
                \textbf{August 2015 - August 2018}
            \end{flushright}
        \end{multicols}

        \vspace{-5mm}

        $\bullet$ {School of Electrical and Electronics Engineering - Research.} \\
        $\bullet$ \textsc{Thesis title}: Implementation of An Autonomous Star Recognition Algorithm using Hardware-Software Co-Processing Approach.


        % --------------- Entry ----------------------------------
        \begin{multicols}{3}
            \begin{flushleft}
                \textbf{Bachelor of Engineering}
            \end{flushleft}

            \columnbreak

            \begin{center}
                \textbf{Vietnam National University HCMC}
            \end{center}

            \columnbreak

            \begin{flushright}
                \textbf{August 2010 - April 2015}
            \end{flushright}
        \end{multicols}

        \vspace{-5mm}

        $\bullet$ {Ho Chi Minh City University of Technology - Electrical and Electronics Engineering - Second Upper Honour} \\
        $\bullet$ {Major in Automation and Control engineering, minor in Robotics and Embedded System Design.} \\
        $\bullet$ \textsc{Thesis title}: Applying of Fuzzy Logic Algorithm on Legged Locomotion Robot.

    % ------------------------- Section: Certificates -------------------------------
    \section{Certificates and Related Courseworks}
        \vspace{-2mm}

        $\bullet$ \textsc{Coursera - \href{https://www.coursera.org/account/accomplishments/specialization/certificate/AKFYZQ9QD8XH}{Data Structures and Algorithms Specialization.}} \\
        $\bullet$ \textsc{Coursera - \href{https://www.coursera.org/account/accomplishments/specialization/certificate/ZUGAFYKCMQ79}{Machine Learning Specialization.}} \\
        $\bullet$ \textsc{Coursera - \href{https://www.coursera.org/account/accomplishments/certificate/G25TQPPNXGW5}{Big Data Essentials: HDFS, MapReduce, and Spark RDD.}} \\
        $\bullet$ \textsc{Coursera - \href{https://www.coursera.org/account/accomplishments/certificate/XN2B7T4AJX8C}{Introduction to Deep Learning.}} \\
        $\bullet$ \textsc{Udacity - \href{https://graduation.udacity.com/confirm/HK9JLR3N}{Machine Learning Engineer Nanodegree.}} \\
        $\bullet$ \textsc{Udacity - \href{https://graduation.udacity.com/confirm/KPSCQGZK}{Full Stack Web Developer Nanodegree.}} \\
        $\bullet$ \textsc{MIT-6.041-Probabilistic Systems Analysis and Applied Probability} \\
        $\bullet$ \textsc{UC Berkeley - CS162 - Operating Systems and Systems Programming} \\
        $\bullet$ \textsc{UIUC - CS425 - Distributed Systems}

    % ------------------------- Section: Competitions -------------------------------
    \section{Competition Achievements}
        \vspace{-2mm}

        $\bullet$ \textsc{Google Code Jam 2018 - Round 2 qualifier - Top 10\% Candidates}


\end{document}
