

\documentclass[10pt]{article}
\usepackage{fontspec}                       %for loading fonts
\usepackage{xunicode,xltxtra,url,parskip}   %other packages for formatting
    \RequirePackage{color,graphicx}
\usepackage{multicol}
\usepackage{titlesec}
\usepackage{hyperref}                       %Setup hyperref package, and colours for links
    \definecolor{linkcolour}{rgb}{0,0.2,0.6}
    \hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}
\usepackage{vwcol}
\usepackage[paperheight=12.2in,paperwidth=9in,top=0.3in,bottom=0.5in,right=0.3in,left=0.3in]{geometry}

%FONTS
\defaultfontfeatures{Mapping=tex-text}
\setmainfont[
    SmallCapsFont = Fontin-SmallCaps.otf,
    BoldFont = Fontin-Bold.otf,
    ItalicFont = Fontin-Italic.otf
]
{Fontin.otf}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}
    \pagestyle{empty}       % non-numbered pages
    \font\fb=''[cmr10]''    %for use with \LaTeX command

    %--------------------TITLE-------------
    \setlength{\columnsep}{1.0cm}
    \begin{multicols}{3}
        \begin{flushleft}
            \textsc Jurong West, \\
            \textsc Singapore, 640953 \\
            \textsc (+65) 8698 0067
        \end{flushleft}

        \columnbreak

        \begin{center}
            \textbf{{\huge Dang Le Dang Khoa }}
        \end{center}

        \columnbreak

        \begin{flushright}
            \href{mailto:dangledangkhoa@gmail.com}{dangledangkhoa@gmail.com} \\
            \href{https://github.com/dangkhoadl}{github.com/dangkhoadl} \\
            \href{https://sg.linkedin.com/in/dangledangkhoa}{linkedin.com/in/dangledangkhoa}
        \end{flushright}
    \end{multicols}

    \vspace{-5mm}

    %--------------------SECTIONS-----------------------------------
    %Section: Education
    \section{Education}

        \vspace{-5mm}

        \begin{multicols}{3}
            \begin{flushleft}
                \textbf{Master of Engineering}
            \end{flushleft}

            \columnbreak

            \begin{center}
                \textbf{Nanyang Technological University}
            \end{center}

            \columnbreak

            \begin{flushright}
                \textbf{August 2015 - Present}
            \end{flushright}
        \end{multicols}

        \vspace{-5mm}

        $\bullet$ {Electrical and Electronics Engineering - Research Program.} \\
        $\bullet$ {Research on Pattern Recognition Algorithms and System implementation for Star Tracker.} \\
        $\bullet$ \textsc{Thesis}: Implementation of An Autonomous Star Recognition Algorithm using Hardware-Software Co-Processing Approach.

        % \vspace{-2mm}

        \begin{multicols}{3}
            \begin{flushleft}
                \textbf{Bachelor of Engineering}
            \end{flushleft}

            \columnbreak

            \begin{center}
                \textbf{Vietnam National University HCMC}
            \end{center}

            \columnbreak

            \begin{flushright}
                \textbf{August 2010 - April 2015}
            \end{flushright}
        \end{multicols}

        \vspace{-5mm}

        $\bullet$ {Ho Chi Minh City University of Technology - Electrical and Electronics Engineering - 2nd Class Upper Honour.} \\
        $\bullet$ {Major in Automation and Control engineering, minor in Robotics and Embedded System Design.} \\
        $\bullet$ \textsc{Thesis}: Applying of Fuzzy Logic Algorithm on Legged Locomotion Robot.

    %Section: Technical Skills
    \section{Languages, Technologies, and Skills}

        \vspace{-2mm}

        $\bullet$ \textbf{Experienced in}: \textsc{C/C++}, \textsc{Python}. \textbf{Familiar with}: \textsc{Bash}, \textsc{SQL}, \LaTeX, \textsc{CSS - HTML}, \textsc{JavaScript}. \\
        $\bullet$ \textsc{Spark}, \textsc{Flask}, \textsc{PostgreSQL}, \textsc{Scipy stacks}, \textsc{Hive}, \textsc{hadoop}. \\
        $\bullet$ \textsc{Data Structures - Algorithms}, \textsc{Problem Solving}, \textsc{Linux/Unix Operating System}, \textsc{System Programming}, \textsc{Machine Learning},\textsc{Big Data}.


    %Section: Experience and Projects
    \section{Project Experience}

        \vspace{-5mm}

        \begin{multicols}{3}
            \begin{flushleft}
                \textbf{Master of Engineering Research}
            \end{flushleft}

            \columnbreak

            \begin{center}
                \textbf{Star Tracking System}
            \end{center}

            \columnbreak

            \begin{flushright}
                \textbf{August 2015 - Present}
            \end{flushright}
        \end{multicols}

        \vspace{-5mm}

        $\bullet$ {Implemented a design of Star Tracking Algorithms onto a Programmable System-on-a-chip system. }\\
        $\bullet$ {Optimized the pattern recognition algorithm runtime by implementing the connected component labeling algorithm on parallel processors. Runtime is improved 64\% on average compared to traditional processor approach.} \\
        $\bullet$ {Optimized and designed the pattern searching algorithm by applying k-ary tree data structure. Time complexity and runtime improved 31\%, but space complexity and memory increased 22\%.} \\
        \textbf{Source code}: \href{https://git.io/vpucY}{git.io/vpucY}

        % \vspace{-2mm}

        \begin{multicols}{3}
            \begin{flushleft}
                \textbf{Bachelor of Engineering Final Year Project}
            \end{flushleft}

            \columnbreak

            \begin{center}
                \textbf{Legged Locomotion Robot}
            \end{center}

            \columnbreak

            \begin{flushright}
                \textbf{June 2014 - January 2015}
            \end{flushright}
        \end{multicols}

        \vspace{-5mm}

        $\bullet$ {Designed and built a 4 Legged Locomotion Robot - trajectory and path planning model.}\\
        $\bullet$ {Developed a system that applies PID algorithm on the robot legging system.}\\
        $\bullet$ {Implemented the Fuzzy Algorithm in C on the balancing system specialized for traversing on inclining terrains.} \\
        $\bullet$ {Designed the sensor and controller software interfaces (step motor encoders, IMU, SPI, UART).} \\
        \textbf{Source code}: \href{https://git.io/vpuCN}{git.io/vpuCN}


        % \vspace{-2mm}

        \begin{multicols}{3}
            \begin{flushleft}
                \textbf{Machine learning Engineer Capstone}
            \end{flushleft}

            \columnbreak

            \begin{center}
                \textbf{Stock Price Predictor}
            \end{center}

            \columnbreak

            \begin{flushright}
                \textbf{March 2018 - April 2018}
            \end{flushright}
        \end{multicols}

        \vspace{-5mm}

        $\bullet$ {Predicted Time-series data by Linear Regression and ARIMA modeling approaches.} \\
        $\bullet$ {Optimized Model's accuracy by 20\% by performing feature engineerings and hyper-parameters optimizations.} \\
        $\bullet$ {Evaluated and Benchmarked models based on Root Mean Squared Error Metrics.} \\
        $\bullet$ {\textbf{Technologies}: pandas, numpy, matplotlib, sklearn.} \\
        \textbf{Source code}: \href{https://git.io/vpulO}{git.io/vpulO}


        \begin{multicols}{3}
            \begin{flushleft}
                \textbf{FullStack Web Developer Capstone}
            \end{flushleft}

            \columnbreak

            \begin{center}
                \textbf{Neighborhood Map APIs}
            \end{center}

            \columnbreak

            \begin{flushright}
                \textbf{September 2017 - October 2017}
            \end{flushright}
        \end{multicols}

        \vspace{-5mm}

        $\bullet$ {Built a neighborhood map based on Google Map, Wikipedia, Foursquare APIs.} \\
        $\bullet$ {Deployed and Configured Amazon Linux servers.} \\
        $\bullet$ {\textbf{Technologies}: Flask, Ajax, jQuery, Knockout.} \\
        \textbf{Source code}: \href{https://git.io/vpuCx}{git.io/vpuCx}

        % \vspace{-2mm}

        \begin{multicols}{3}
            \begin{flushleft}
                \textbf{Side Projects}
            \end{flushleft}

            \columnbreak

            \begin{center}
                \textbf{GitHub Projects}
            \end{center}

            \columnbreak

            \begin{flushright}
                \textbf{August 2010 - Present}
            \end{flushright}
        \end{multicols}

        \vspace{-5mm}

        $\bullet$ {Algorithm Handbook - Solved nearly 100 Google Code Jam problems - \textbf{Source code}: \href{https://git.io/vpuWf}{git.io/vpuWf}.} \\
        $\bullet$ {Machine Learning projects  - \textbf{Source code}: \href{https://git.io/vpuWJ}{git.io/vpuWJ}.} \\
        $\bullet$ {Big Data, Distributed System projects - \textbf{Source code}: \href{https://git.io/vpuWU}{git.io/vpuWU}.} \\
        $\bullet$ {Robotics projects - \textbf{Source code}: \href{https://git.io/vpuWT}{git.io/vpuWT}.}


    %Section: Certificates
    \section{Certificates}

    \vspace{-2mm}

    $\bullet$ \textsc{Coursera - \href{https://www.coursera.org/account/accomplishments/specialization/certificate/AKFYZQ9QD8XH}{Data Structures and Algorithms Specialization} - UC Sandiego, National Research University HSE} - \textbf{Certificate}: \href{https://bit.ly/2rebiVI}{bit.ly/2rebiVI}. \\
    $\bullet$ \textsc{Coursera - \href{https://www.coursera.org/account/accomplishments/specialization/certificate/ZUGAFYKCMQ79}{Machine Learning Specialization} - University of Washington} - \textbf{Certificate}: \href{https://bit.ly/2HJjTG9}{bit.ly/2HJjTG9}.\\
    $\bullet$ \textsc{Coursera - \href{https://www.coursera.org/account/accomplishments/certificate/G25TQPPNXGW5}{Big Data Essentials: HDFS, MapReduce, and Spark RDD} - Yandex} - \textbf{Certificate}: \href{https://bit.ly/2JMHNBr}{bit.ly/2JMHNBr}. \\
    $\bullet$ \textsc{Coursera - \href{https://www.coursera.org/account/accomplishments/certificate/XN2B7T4AJX8C}{Introduction to Deep Learning} - National Research University HSE} - \textbf{Certificate}: \href{https://bit.ly/2jnra44}{bit.ly/2jnra44}. \\
    $\bullet$ \textsc{Udacity - \href{https://graduation.udacity.com/confirm/HK9JLR3N}{Machine Learning Engineer Nanodegree}} - \textbf{Certificate}: \href{https://bit.ly/2jkFsSQ}{bit.ly/2jkFsSQ}. \\
    $\bullet$ \textsc{Udacity - \href{https://graduation.udacity.com/confirm/KPSCQGZK}{Full Stack Web Developer Nanodegree}} - \textbf{Certificate}: \href{https://bit.ly/2w2Z0EG}{bit.ly/2w2Z0EG}.

    %Section: Honors and Awards
    \section{Honors and Awards}

    \vspace{-2mm}

        $\bullet$ \textbf{Google Code Jam 2018} - Round 2 Qualifier - top 10\% among all candidates
\end{document}
