\section{Experience}
\vspace{-2mm}

% --------------- Entry ----------------------------------
\begin{multicols}{3}
    \begin{flushleft}
        \textbf{Senior Research Engineer}
    \end{flushleft}

    \columnbreak

    \begin{center}
        \textbf{Institute for Infocomm Research (I2R) - A*STAR}
    \end{center}

    \columnbreak

    \begin{flushright}
        \textbf{February 2020 - Present}
    \end{flushright}
\end{multicols}

\vspace{-5mm}

\emph{Automatic Speech Recognition (ASR)}
\vspace{-2.5mm}
\begin{itemize}[noitemsep]
    \item Trained and maintained Multilingual South East Asia ASR engines and language models, reduced the WERs by 10\% compared to the baseline models.
    \item Finetuned and adapted entity localization ASR engines into domain-specific services, including Legal, Aviation Control, and Education. Featured project: Intelligent Court Transcription System - \href{https://www.straitstimes.com/singapore/courts-crime/state-courts-to-use-system-that-instantly-transcribes-court-proceedings}{External-URL}.
    \item Analyzed and benchmarked the quality of audio and text data, handled the data preprocessing, augmentation, and engineering pipeline.
\end{itemize}

\emph{Natural Language Processing (NLP) - Speech and Audio Analytics}
\vspace{-2.5mm}
\begin{itemize}[noitemsep]
    \item Trained and deployed the ECAPA-TDNN deep learning model for a speaker diarization inference service, achieved a 5\% decrease in EER compared to the baseline X-Vectors model.
    \item Trained and deployed U-net speech enhancement model for Satellite-based VHF communication, improved the AUC by 3\% compared to the baseline RNN model.
    \item Contributed to internal tools and APIs, including Transformer-based Sentiment Analysis, Embedded Sound Classification, Vietnamese-voiced FAQ LLM-based chatbot, etc.
\end{itemize}

% --------------- Entry ----------------------------------
\begin{multicols}{3}
    \begin{flushleft}
        \textbf{Researcher}
    \end{flushleft}

    \columnbreak

    \begin{center}
        \textbf{Satellite Research Centre}
    \end{center}

    \columnbreak

    \begin{flushright}
        \textbf{August 2016 - August 2018}
    \end{flushright}
\end{multicols}

\vspace{-5mm}

% \begin{itemize}[noitemsep,leftmargin=*]
\begin{itemize}[noitemsep,leftmargin=*]
    \item Implemented a novel Star Tracking Algorithm onto a Programmable System-on-a-chip for mini satellites.
    \item Optimized the pattern recognition algorithm runtime, improved the accuracy by 5\% on average.
    \item Designed a tree-based pattern searching algorithm that enhanced runtime processing by 25\%.
\end{itemize}
