\section{Projects}
\vspace{-2mm}
% --------------- Entry ----------------------------------
\begin{multicols}{1}
    \begin{flushleft}
        \textbf{VLSP 2023 Challenge - ASR}
    \end{flushleft}
\end{multicols}

\vspace{-5mm}

\indent VLSP 2023 Vietnamese ASR is a challenge subtrack that requires participating teams to tackle an ASR problem in the Vietnamese language, with the constraint of noisy and limited-size datasets. My contributions to the team include:
\vspace{-1.5mm}
\begin{itemize}[noitemsep]
    \item Leading the team to address the ASR combined with Emotion Classification problem.
    \item Designing and implementing an end-to-end solution for training and distilling ASR models with small datasets.
    \item \emph{Challenge Description}: \href{https://vlsp.org.vn/vlsp2023/eval/asr}{https://vlsp.org.vn/vlsp2023/eval/asr}
\end{itemize}
% \vspace{-2mm}

% --------------- Entry ----------------------------------
\begin{multicols}{1}
    \begin{flushleft}
        \textbf{Vessenger AI}
    \end{flushleft}
\end{multicols}

\vspace{-5mm}

\indent Vessenger AI is a web-based application that assists clients in managing meeting minutes. Its functions include recording, transcribing, translating, and diarizing speakers in a multilingual, team-based meeting scenario. My responsibilities include: \looseness=-1
\vspace{-1.5mm}
\begin{itemize}[noitemsep]
    \item Deployed the Speaker Diarization Inference API.
    \item Maintained the interfacing and preprocessing backend services.
    \item \emph{Demo Application URL}: \href{https://devaliasr.kkode.com/home/beta7}{https://devaliasr.kkode.com/home/beta7}
\end{itemize}
% \vspace{-2mm}

% --------------- Entry ----------------------------------
\begin{multicols}{1}
    \begin{flushleft}
        \textbf{WER-in-CPP}
    \end{flushleft}
\end{multicols}

\vspace{-5mm}

\indent WER-in-CPP is my personal open-source program that computes and represents ASR Word-Error-Rate metrics in the text-based format.
\vspace{-1.5mm}
\begin{itemize}[noitemsep]
    \item Developed and implemented algorithms based on the Minimum-Edit-Distance Dynamic Programming problem.
    \item Designed the text-based visualization and added features for statistical analysis.
    \item \emph{Source code}: \href{https://github.com/dangkhoadl/WER-in-cpp}{github.com/dangkhoadl/WER-in-cpp}
\end{itemize}
% \vspace{-2mm}

% --------------- Entry ----------------------------------
% \begin{multicols}{1}
%     \begin{flushleft}
%         \textbf{Machine Learning and Algorithms Repositories}
%     \end{flushleft}
% \end{multicols}
% \vspace{-5mm}
% \begin{itemize}[noitemsep]
%     \item Maintain GitHub repositories for personal note-taking, introducing and mentoring students to Data Structures - Algorithms, and Machine Learning.
%     \item Solved multiple problems in Computer science (Traveling Salesman, Stable Marriage Matching, etc.) and Machine Learning (Random Walks, AI bot playing the trending mobile game \emph{Lyto Different Color}).
%     \item \emph{Data structures and Algorithms implementation}: \href{https://github.com/dangkhoadl/my-CS-Notebook}{github.com/dangkhoadl/my-CS-Notebook}
%     \item \emph{Discrete Optimization Algorithms implementation}: \href{https://github.com/dangkhoadl/Coursera-Discrete-Optimization}{github.com/dangkhoadl/Coursera-Discrete-Optimization}
%     \item \emph{Machine Learning and Deep Learning models implementation}: \href{https://github.com/dangkhoadl/Machine-Learning-model-implementation}{github.com/dangkhoadl/Machine-Learning-model-implementation}
% \end{itemize}
% \vspace{-2mm}

% --------------- Entry ----------------------------------
